% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%


% truth -> i / l validity 
% Vdash -> ...
% hypotesis
% Capitalize all - the for ... 
\documentclass[runningheads]{llncs}


\usepackage{amssymb}%
\usepackage{amsmath}
\usepackage{bussproofs}
\usepackage{tikz}
\usepackage[T1]{fontenc}

\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage{graphicx}


% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\input{figures_and_tables}
\input{theorems_and_definitions}
\begin{document}
%
\title{Translating from Tableaux Proofs into Sequent Proofs in Classical and Intuitionistic Logic}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Ian Ribeiro\inst{1} \and
Olivier Hermant \inst{2} }
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{MINES ParisTech, PSL Research University, France
\email{ian.ribeiro\_de\_faria\_leite@minesparis.psl.eu}\\
\and
MINES ParisTech, PSL Research University, France\\
\email{olivier.hermant@mines-paristech.fr *(Q1)}} %[Question? cest un rapport ]
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
This work aims to discuss the translation between Tableaux proofs and sequent calculus proofs in both first-order intuitionistic predicate logic and in first-order classical predicate logic.
It begins with an overview of the definitions in both intuitionistic and classical logic.
It then shows a translation process in classical logic and its OCAML implementation restricted to propositional logic. 
Finally, a potential extension towards translation in intuitionistic logic is discussed.
 \keywords{Tableaux proof  \and  sequent calculus  \and intuitionistic logic.}
\end{abstract}
%
%
%
\section{Introduction}
\subsection{Notation}


%See Figure~\ref{fig:first} and Figure~\ref{fig:second}. asdf %

In this work, sentences will implicitly refer to first-order predicate logic sentences; for intuitionistic logic, their meaning will come from Kripke's semantics \cite{kripke1965} . The notation for structures and frames will be heavily based on \cite{book1}. 
In order to make this document slightly more self-reliant and to clarify the notation, and we will briefly explain:
\subsection{Definitions}
%(TODO how detailed? < or > than thepresentation? )

\structureDefinition
Structures represent possible worlds or possible states of knowlege inside a frame:
\kripkeFrameDefinition

Particularlly, in order to simplify the notation, R will always be the set of sequences of integers, and $p \leq q$ if it exists an $l$ such that $q =  p||l$  . Also,    
 Also, from now on, the constant elements of a language will allways be in the ordered set $\{c_0, c_1, c_2 ...\}$
 
 \figureRandFrame

\forcingDefinition

\intuitionisticValidityDefinition

In classical logic, this definition simplifies to the one of forcing, and it's simplified again by the fact that p = q; in fact, here we will define classical validity as: \cite{book1}

\classicalValidityDefinition

\section{The intuitionistic tableaux method}

\subsubsection{Considerations}
    Here we first define a slightly different version of the destructive tableaux proof tree described by \cite{book1}, where each node is a truth assertion. Thi different version  will allow for a more implementation-oriented approach and the translation later on.

    The correspondence of the destructive tableaux proof tree described in \cite{book1} to our new one is shown in Figure \ref{fig:destructive_tableaux}. Generally speaking, a node in the usual definition is replaced by a sequence of all nodes in the path that goes from the root to it. Afterwards, some nodes are removed from the newly formed tableaux by adjoining its son(s) and its parent. A node should be removed if its corresponding node in the original tableaux was not a leaf of the atomic tableaux \cite{book1} that introduced it.


    \tableauxCumulativeAndNonCumulativeExampleFigure
    In this new presentation, one can see each node of the tree as an assumption of the existence of 
    a frame that respects a list of constraints, and each edge as an implication between assumptions.
\subsubsection{The Intuitionistic tableaux method }
The tableaux stands on some definitions, they will be justified briefly:
\begin{definition}
    \textbf{A Signed sentence} is a forcing assertion inside of a tableaux proof. It looks like $T_{q} \phi $ or $F_{p} \phi $ \\
    \textbf{A Signed sentence list} is a list forcing assertions inside of a tableau proof. We say that a list of forcing assertions having sentences $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
  and $ \{F_{q_1}\delta_{1}, F_{q_2}\delta_{2}...\} $
     is "intuitionistically valid" (Question 2: maybe use a term != valid?)if there exists a frame $\mathcal{C}$ for which $ \mathcal{C}(p_1) \Vdash \gamma_{1}$ and $ \mathcal{C}(p_{2}) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(q_{1}) \nvDash \delta_{1}$  and $ \mathcal{C}(q_{2}) \nvDash \delta_{2}$
\end{definition}
 

A Signed sentence list can be seen as an existance assumption that may or may not be intuitionistically valid. We can infer other assumptions that are, by definition, 
consequences of a given assumption. The function f, defined bellow, is one of the ways we can do that: 




\begin{definition}
    The function $f$ takes a signed sentence $\sigma$ and a signed sentence list $L$ and returns one or two signed sentence lists.  \\$f(\sigma,L)$ is defined as follows:
    \\(here we denote $l||l'$ = $l_1,l_2...,l_{|l|}, l'_1,l'_2..,l'_{|l'|} $)
    \\if $\sigma \in L$:
        \begin{itemize}
            \item $f(T_{p} \neg \alpha,L) = [L - \sigma|| \sigma || F_{p'}\alpha] $ \\ for a $p' \geq p$ not in $h||L$.
            \item $f(F_{p} \neg \alpha,L) = [L - \sigma || \sigma || T \alpha]$ \\for the first $p' \geq p$ for such that $F \neg \alpha$ is not in $L$.
            \item $f(T_{p} (\alpha \land \beta), L) = [L - \sigma|| \sigma || T_{p} \alpha || T_{p} \beta]$.
            \item $f(F_{p} (\alpha \land \beta), L) = [L - \sigma|| \sigma || F_{p} \alpha],[ L || h || F_{p} \beta]$.
            \item $f(T_{p} (\alpha \lor \beta), L) = [L - \sigma|| \sigma || T_{p} \alpha],[ L || h || T_{p} \beta]$.
            \item $f(F_{p} (\alpha \lor \beta), L) = [L - \sigma|| \sigma || F_{p} \alpha || F_{p} \beta]$.
            \item $f(T_{p} (\alpha \to \beta), L) = [L - \sigma|| \sigma || F_{p'} \alpha],[ L || h || T_{p'} \beta]$ \\for the first $p' \geq p$ such that  $F \neg \alpha$ is not in $L$.
            \item $f(F_{p} (\alpha \to \beta), L) = [L - \sigma|| \sigma || T_{p'} \alpha || F_{p'} \beta]$ \\for a $p' \geq p$ not in $h||L$.
            \item $f(T_{p} (\forall x) \phi(x), L) = [L - \sigma|| \sigma || T_{p} \phi(c_i) ]$\\ for the first constant $c_i$ for which $T_{p} \phi(c_i)$ is not in $L$.
            \item $f(F_{p} (\forall x) \phi(x), L) = [L - \sigma|| \sigma || F_{p} \phi(c_i) ]$\\ for the first constant $c_i$ not present in $h||L$.
            \item $f(T_{p} (\exists x) \phi(x), L) = [L - \sigma|| \sigma || T_{p} \phi(c_i) ]$ \\for the first constant $c_i$ not present in $h||L$.
            \item $f(F_{p} (\exists x) \phi(x), L) = [L - \sigma|| \sigma || F_{p} \phi(c_i) ]$\\ for the first constant $c_i$ such that $F_{p} \phi(c_i)$ is not in $L$.
        \end{itemize} [TODO revise]\\
    if $\sigma \notin L$:
    \begin{itemize}
         \item $f(\sigma,L) = L $
    \end{itemize}
\end{definition}


Allthough not justified here, the reordering of the terms plays an important role in the implementation and in the completnees of the sistematic tableaux. On the other hand, 
the soundness of the tableaux method depends on the fact that f is "well behaved":
\begin{theorem}
    Given a signed sentence list x, if x is intuitionistically valid then f(x) is intuitionistically valid 
\end{theorem}
\begin{proof}
    \cite{book1} proves this by using the definition of forcing. The choices of $p'$ and $c_i$ garantes the completnees of the tableaux.
     [TODO]
\end{proof}


\begin{definition}
    \textbf{The Tableux development of a sentence } is defined inductivelly: 
    \begin{itemize}
        \item A tree with the single node $\{F \phi \}$ is a tableaux development of $\phi$. 
        \item If $\tau$ is a tableaux development of $\phi$, then $\hookleftarrow(\sigma,\tau)$ is a tableaux development of $\phi$. Where:
    \end{itemize}

    $\hookleftarrow(\sigma,\tau) = $ $\tau$ with $f(\sigma, l) $added to all leaves l that contain $\sigma$

\end{definition}



\begin{figure}
    \centering
    \makebox[\textwidth][c]{%
    \resizebox{0.95\textwidth}{!}{
    
    \begin{tikzpicture}[scale=0.9]
    \node {$F \phi$}
        child {node {$\ldots$}
            child {node {$\ldots$}}
            child {node {$T \neg \alpha, ...$}
                child {node {$F \alpha, ... T \neg \alpha$}}}
            child {node {$\ldots$}}
            child {node {$T \neg \alpha, ...$}
                child {node {$F \alpha, ... T \neg \alpha$}}}};
    \end{tikzpicture}%
    
    
    
    \hspace{0.5cm} \raisebox{1.8cm}{$\hookleftarrow$} 
    \hspace{0.5cm}
    \raisebox{1.25cm}{
    \begin{tikzpicture}[scale=0.9]
    \node {$F \phi$}
        child {node {$\ldots$}
            child {node {$\ldots$}}
            child {node {$T \neg \alpha, ...$}}
            child {node {$\ldots$}}
            child {node {$T \neg \alpha, ...$}}};
    \end{tikzpicture}
    }
    %
    }%
    }
    \caption{Example of $\hookleftarrow(T \neg \alpha ,\tau)$ and $\tau$ } 
    \label{fig:tree_expansion}
    \end{figure}
    

    % \begin{definition} 
    %     A tree with the single node $\{F \phi \}$ is a tableaux development of $\phi$. \\
    % 
    %     if $\tau$ is a tableaux development of $\phi$ then $\hookleftarrow(\sigma,\tau)$ is a tableaux development of $\phi$.
    % We define the function $\hookleftarrow$: 
    %     
    %     Given a signed sentence $\sigma$ and a tableaux development $\tau$ of $\phi$ :
    %     (here we denote $l||l'$ = $l_1,l_2...,l_{|l|}, l'_1,l'_2..,l'_{|l'|} $)
    %     \begin{itemize}
    %         \item $\hookleftarrow(T \neg \alpha,\tau) = \tau$ with the node $t || h || F \alpha $ 
    %         added to all leaves $h||t$ that contain $T\neg \alpha$.
    %         \item $f(F \neg \alpha,\tau) = \tau$ with $L : \{T \alpha\}$ 
    %         added (adjoined?) to all leaves $L$ that contain $F \neg \alpha$.
    %         \item $f(T (\alpha \land \beta),\tau) = \tau$ with $L : \{T \alpha, T \beta\}$ 
    %         added to all leaves $L$ that contain $T (\alpha \land \beta)$.
    %         \item $f(F (\alpha \land \beta),\tau) = \tau$ with $L : \{F \alpha\}$ and $L : \{F \beta\}$ 
    %         added to all leaves $L$ that contain $F (\alpha \land \beta)$.
    %         \item $f(T (\alpha \lor \beta),\tau) = \tau$ with $L : \{T \alpha\}$ and $L : \{T \beta\}$ 
    %         added to all leaves $L$ that contain $T (\alpha \lor \beta)$.
    %         \item $f(F (\alpha \lor \beta),\tau) = \tau$ with $L : \{F \alpha, F \beta\}$ 
    %         added to all leaves $L$ that contain $F (\alpha \lor \beta)$.
    %         \item $f(T (\alpha \to \beta),\tau) = \tau$ with $L : \{F \alpha\}$ and $L : \{T \beta\}$ 
    %         added to all leaves $L$ that contain $T (\alpha \to \beta)$.
    %         \item $f(F (\alpha \to \beta),\tau) = \tau$ with $L : \{T \alpha, F \beta\}$ 
    %         added to all leaves $L$ that contain $F (\alpha \to \beta)$.
    %      \end{itemize}
    % \end{definition}




\begin{theorem}
    If $F\phi$ is intuitionistically valid then one of the leaves of $ \hookleftarrow (\sigma_n,\hookleftarrow(\sigma_{n-1}(.....(\hookleftarrow(\sigma_1 , )...)))) $ is intuitionistically valid.
\end{theorem}

\begin{proof}

    The proof goes by induction:


             The base case is true by definition: either the root $F\phi$ is a intuitionistically valid leaf or the premisse is false.  Next we assume $\tau' = \hookleftarrow (\sigma, \tau)$.
             There are two cases to consider:
            \begin{itemize}
                \item If there does not exist a frame that does not force $\phi$, $F\phi$ is not intuitionistically valid and the theorem holds for $\tau'$.
                \item  If there exists a frame that does not force $\phi$:

                         By the induction hypothesis, there exists a intuitionistically valid leaf $\sigma$ in $\tau$.
                         \begin{itemize}
                    \item If $\sigma$ is a leaf in $\tau$, then $F\phi$ the theorem holds for $\tau'$.
                    \item If $\sigma$ is not a leaf in $\tau$, then:
                         One or two nodes were added to $\sigma$ in $\tau'$ by the definition of $\hookleftarrow$.
                         By the theorem 1, one of the added nodes is also intuitionistically valid.
                         Consequently, the theorem holds for $\tau'$.

            \end{itemize}
            \end{itemize}
    \end{proof}

    From this, we can conlude that: 
        If all leaves of $ \hookleftarrow (\sigma_n,\hookleftarrow(\sigma_{n-1}(.....(\hookleftarrow(\sigma_1 , F\phi)...)))) $ are contradictory, then $F\phi$ is not intuitionistically valid, by consequence 
        $\phi$ is intuitionistically valid. 



\subsubsection{completnees }

For purposes of implementation, we define an $\hookleftarrow_c$ that can be applied systematically: 
\begin{definition}
     $\hookleftarrow_c(\tau) = \tau$ with $f(h,l)$ added to all leaves l that contain $\sigma$. h is the first signed sentence of the shalowest non-contradictory leaf. 
\end{definition}
we can use $\hookleftarrow_c$ instead of $\hookleftarrow$ to define a sistematic tableaux

[TODO]

\section{The classical tableaux method}

The classical tableaux method can be seen as a the intuitionistic tableaux method restricted to 
one-framed structures. The adapted definitions are: 



\begin{definition}
    \textbf{A Signed sentence} is a forcing assertion inside of a tableaux proof. It looks like $T \phi $ or $F \phi $ \\
    \textbf{A Signed sentence list} is a list forcing assertions inside of a tableau proof. We say that a list of forcing assertions having sentences $\{ T\gamma_{1}, T\gamma_{2}, ...\}$
  and $ \{F\delta_{1}, F\delta_{2}...\} $
     is "classically valid" (Question 2: maybe use a term != valid?)if there exists a single-structured frame  $\mathcal{C}$ such that $ \mathcal{C}(\emptyset) \Vdash \gamma_{1}$ and $ \mathcal{C}(\emptyset) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(\emptyset) \nvDash \delta_{1}$  and $ \mathcal{C}(\emptyset) \nvDash \delta_{2}$
\end{definition}
 


\begin{definition}
    The function $f$ takes a signed sentence $\sigma$ and a signed sentence list $L$ and returns one or two signed sentence lists.  \\$f(\sigma,L)$ is defined as follows:
    \\(here we denote $l||l'$ = $l_1,l_2...,l_{|l|}, l'_1,l'_2..,l'_{|l'|} $)
    \\if $\sigma \in L$:
        \begin{itemize}
            \item $f(T \neg \alpha,L) = [L - \sigma|| \sigma || F \alpha]$.
            \item $f(F \neg \alpha,L) = [L - \sigma || \sigma || T \alpha]$.
            \item $f(T (\alpha \land \beta), L) = [L - \sigma|| \sigma || T \alpha || T \beta]$.
            \item $f(F (\alpha \land \beta), L) = [L - \sigma|| \sigma || F \alpha],[ L || \sigma || F \beta]$.
            \item $f(T (\alpha \lor \beta), L) = [L - \sigma|| \sigma || T \alpha],[ L || \sigma || T \beta]$.
            \item $f(F (\alpha \lor \beta), L) = [L - \sigma|| \sigma || F \alpha || F \beta]$.
            \item $f(T (\alpha \to \beta), L) = [L - \sigma|| \sigma || F \alpha],[ L || \sigma || T \beta]$.
            \item $f(F (\alpha \to \beta), L) = [L - \sigma|| \sigma || T \alpha || F \beta]$.
            \item $f(T (\forall x) \phi(x), L) = [L - \sigma|| \sigma || T \phi(c_i)]$ \\ for the first constant $c_i$ for which $T \phi(c_i)$ is not in $L$.
            \item $f(F (\forall x) \phi(x), L) = [L - \sigma|| \sigma || F \phi(c_i)]$ \\ for the first constant $c_i$ not present in $L$.
            \item $f(T (\exists x) \phi(x), L) = [L - \sigma|| \sigma || T \phi(c_i)]$ \\ for the first constant $c_i$ not present in $L$.
            \item $f(F (\exists x) \phi(x), L) = [L - \sigma|| \sigma || F \phi(c_i)]$ \\ for the first constant $c_i$ for which $F \phi(c_i)$ is not in $L$.
        \end{itemize} [TODO revise] \\
    if $\sigma \notin L$:
    \begin{itemize}
         \item $f(\sigma,L) = L $
    \end{itemize}
\end{definition}




\section{Sequent calculus}
    Here we use the multi-conclusion sequent calculus defined by \cite{book2}. 
    
\begin {definition}
    \textbf{Sequent} A sequent is an expression of the form 
    \[
    \Gamma \vdash \Delta
    \]
    where $\Gamma = \{\Gamma_1, \Gamma_2, \Gamma_3,...\}$ and $\Delta = \{\Delta_1,\Delta_2,\Delta_3 ...\}$
     are  finite sets of formulas. $\Gamma $ is called the antecedent, and 
    $\Delta$ is called the succedent. 
\end {definition}


$\Gamma $ represents multiple necessary hipotesis, while $\Delta$ represents multiple possible conclusions. 
\begin {definition}
A sequent is intuitionistically valid if for all kripke frames, if $\Gamma$ are forced, then at least one of $\Delta$ is forced.
\end {definition}
\paragraph{}
The more akward definition:


"
A sequent is classically valid if , there does not exist a single-sentenced frame 
that forces all sentences in $\Gamma$ and does not force any sentence in $\Delta$.
"

when compared with the definition of list of signed sentences, hints us towards a semantical equivalence for single framed structures, wich will not be discussed in depth. 

\paragraph{}
The meaning of a sequent calculus rule is [Question : is "meaning" too strong? -> maybe change to "a sequent calculus rule can be interpreted as"] the implication: if the top sequent is 
 valid, then the botton sequent is valid.
 
Sintatically [question sintaxically ? ], each of the rules represent veriticies that can be added to a sequent proof tree development 
to obtain another sequent proof tree development




\subsection {Classical Sequent calculus}

\begin {definition}
    A single sequent is a classical sequent proof tree development\\
    Any of the rules of the table 1 aplied to a classical sequent proof tree development is a sequent proof tree development\\
    A classical squent proof tree is a classical sequent proof tree development with axioms on all leafs.
\end {definition} 

Rules for classical multi-consequence sequent calculus are given in the table \ref{tab1}

\begin{table}[h!]
    \caption{Cumulative Sequent Calculus Rules (Multi-Consequence)}\label{tab:cumulative}
    \centering
    \renewcommand{\arraystretch}{3}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Rule} & \textbf{Inference} \\ \hline
        Axiom & $\AxiomC{}\UnaryInfC{$\Gamma, \phi \vdash \phi, \Delta$}\DisplayProof$ \\ \hline
        
        Weakening & 
        $\AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma, \phi \vdash \Delta$}\DisplayProof$ \quad
        $\AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma \vdash \Delta, \phi$}\DisplayProof$ \\ \hline
        
        Negation & 
        $\RightLabel{\scriptsize{$\neg$R}}\AxiomC{$\Gamma , \neg \phi \vdash \phi, \Delta$}\UnaryInfC{$\Gamma, \neg \phi \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\neg$L}}\AxiomC{$\Gamma, \phi \vdash \Delta, \neg \phi $}\UnaryInfC{$\Gamma \vdash  \Delta, \neg \phi $}\DisplayProof$ \\ \hline
        
        Conjunction & 
        $\RightLabel{\scriptsize{$\land$L}}\AxiomC{$\Gamma, \phi, \psi, \phi \land \psi \vdash \Delta$}\UnaryInfC{$\Gamma, \phi \land \psi \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\land$R}}\AxiomC{$\Gamma \vdash \phi, \phi \land \psi,\Delta$}\AxiomC{$\Gamma \vdash \psi, \phi \land \psi,\Delta$}\BinaryInfC{$\Gamma \vdash \phi \land \psi, \Delta$}\DisplayProof$ \\ \hline
        
        Disjunction & 
        $\RightLabel{\scriptsize{$\lor$L}} \AxiomC{$\Gamma, \phi \lor \psi,\phi \vdash \Delta$}\AxiomC{$\Gamma, \phi \lor \psi,\psi \vdash \Delta$}\BinaryInfC{$\Gamma, \phi \lor \psi \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\lor$R}} \AxiomC{$\Gamma \vdash \phi \lor \psi, \psi, \Delta$}\UnaryInfC{$\Gamma \vdash \phi \lor \psi, \Delta$}\DisplayProof$ \\ \hline
        
        Implication & 
        $\RightLabel{\scriptsize{$\to$L}} \AxiomC{$\Gamma, \phi \to \psi \vdash \phi, \Delta$}\AxiomC{$\Gamma, \phi \to \psi, \psi \vdash \Delta$}\BinaryInfC{$\Gamma, \phi \to \psi \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\to$R}} \AxiomC{$\Gamma, \phi \vdash \psi, \phi \to \psi, \Delta$}\UnaryInfC{$\Gamma \vdash \phi \to \psi, \Delta$}\DisplayProof$ \\ \hline
        
        Quantifiers & 
        $\RightLabel{\scriptsize{$\forall$L}} \AxiomC{$\Gamma, \forall x \phi(x), \phi(t) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \phi(x) \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\forall$R}} \AxiomC{$\Gamma \vdash \phi(y), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \phi(x), \Delta$}\DisplayProof$ \\
        & 
        $\RightLabel{\scriptsize{$\exists$L}} \AxiomC{$\Gamma, \phi(y) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \phi(x) \vdash \Delta$}\DisplayProof$ \quad
        $\RightLabel{\scriptsize{$\exists$R}} \AxiomC{$\Gamma \vdash \phi(t), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \phi(x), \Delta$}\DisplayProof$ \\ \hline
    \end{tabular}
\end{table}


\begin{table}[h!]
    \caption{Rules for L's classical multi-consequence sequent calculus}\label{tab2}
\centering
\renewcommand{\arraystretch}{3} % Adjust row height
\begin{tabular}{|c|c|}
\hline
\textbf{Rule} & \textbf{Inference} \\ \hline
Axiom  & $\AxiomC{}\UnaryInfC{$\alpha \vdash \alpha$}\DisplayProof$ \\ \hline
Weakening & $ \AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \vdash \Delta$}\DisplayProof$ \quad
$\AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma \vdash \Delta, \alpha$}\DisplayProof$ \\ \hline
Negation & 
$\RightLabel{\scriptsize{$\neg$R  $\neg \alpha$}}\AxiomC{$\Gamma , \vdash \alpha, \Delta$}\UnaryInfC{$\Gamma, \neg \alpha \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\neg$L  $\neg \alpha$}}\AxiomC{$\Gamma, \alpha \vdash \Delta$}\UnaryInfC{$\Gamma \vdash \neg \alpha, \Delta$}\DisplayProof$ \\ \hline
Conjunction & 
$\RightLabel{\scriptsize{$\land$L  $\alpha \land \beta$}}\AxiomC{$\Gamma, \alpha, \beta \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \land \beta \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\land$R $\alpha \land \beta$}}\AxiomC{$\Gamma \vdash \alpha, \Delta$}\AxiomC{$\Gamma \vdash \beta, \Delta$}\BinaryInfC{$\Gamma \vdash \alpha \land \beta, \Delta$}\DisplayProof$ \\ \hline
Disjunction & 
$\RightLabel{\scriptsize{$\lor$ L  $\alpha \lor \beta$}}\AxiomC{$\Gamma, \alpha \vdash \Delta$}\AxiomC{$\Gamma, \beta \vdash \Delta$}\BinaryInfC{$\Gamma, \alpha \lor \beta \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\lor$ R  $\alpha \lor \beta$}}\AxiomC{$\Gamma \vdash \alpha, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\lor$ R  $\alpha \lor \beta$}}\AxiomC{$\Gamma \vdash \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$ \\ \hline
Implication & 
$\RightLabel{\scriptsize{$\to$ L  $\alpha \to \beta$}}\AxiomC{$\Gamma \vdash \alpha, \Delta$}\AxiomC{$\Gamma, \beta \vdash \Delta$}\BinaryInfC{$\Gamma, \alpha \to \beta \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\to$ R  $\alpha \to \beta$}}\AxiomC{$\Gamma, \alpha \vdash \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \to \beta, \Delta$}\DisplayProof$ \\ \hline
Quantifiers & 
$\RightLabel{\scriptsize{$\forall$ L $\forall x \alpha(x)$}}\AxiomC{$\Gamma, \alpha(t) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \alpha(x) \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\forall$ R $\forall x \alpha(x)$}}\AxiomC{$\Gamma \vdash \alpha(y), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \alpha(x), \Delta$}\DisplayProof$ \\ 
& 
$\RightLabel{\scriptsize{$\exists$ L $\exists x \alpha(x)$}}\AxiomC{$\Gamma, \alpha(y) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \alpha(x) \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\exists$ R $\exists x \alpha(x)$}}\AxiomC{$\Gamma \vdash \alpha(t), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \alpha(x), \Delta$}\DisplayProof$ \\ \hline
Contraction & 
$\AxiomC{$\Gamma, \alpha, \alpha \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \vdash \Delta$}\DisplayProof$ \quad
$\AxiomC{$\Gamma \vdash \alpha, \alpha, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha, \Delta$}\DisplayProof$ \\ \hline
\end{tabular}
\end{table}


\subsection {Intuitionistic Sequent calculus}
\begin {definition}
    A single sequent is a intuitionistic sequent proof tree development\\
    Any of the rules of the table 1 aplied to a intuitionistic sequent proof tree development is a sequent proof tree development\\
    A intuitionistic squent proof tree is a intuitionistic sequent proof tree development with axioms on all leafs.
\end {definition} 


Rules for L's intuitionistic multi-consequence sequent calculus are given in \ref{tab2}


\begin{table}[h!]
    \caption{Rules for L's intuitionistic multi-consequence sequent calculus}\label{tab2}
\centering
\renewcommand{\arraystretch}{3} % Adjust row height
\begin{tabular}{|c|c|}
\hline
\textbf{Rule} & \textbf{Inference} \\ \hline
Axiom  & $\AxiomC{}\UnaryInfC{$\phi \vdash \phi$}\DisplayProof$ \\ \hline
Weakening & $ \AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma, \phi \vdash \Delta$}\DisplayProof$ \quad
$\AxiomC{$\Gamma \vdash \Delta$}\UnaryInfC{$\Gamma \vdash \Delta, \phi$}\DisplayProof$ \\ \hline
Negation & 
$\RightLabel{\scriptsize{$\neg$R  $\neg \phi$}}\AxiomC{$\Gamma , \vdash \phi, \Delta$}\UnaryInfC{$\Gamma, \neg \phi \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\neg$L  $\neg \phi$}}\AxiomC{$\Gamma, \phi \vdash \Delta$}\UnaryInfC{$\Gamma \vdash \neg \phi, \Delta$}\DisplayProof$ \\ \hline
Conjunction & 
$\RightLabel{\scriptsize{$\land$L  $\phi \land \psi$}}\AxiomC{$\Gamma, \phi, \psi \vdash \Delta$}\UnaryInfC{$\Gamma, \phi \land \psi \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\land$R $\phi \land \psi$}}\AxiomC{$\Gamma \vdash \phi, \Delta$}\AxiomC{$\Gamma \vdash \psi, \Delta$}\BinaryInfC{$\Gamma \vdash \phi \land \psi, \Delta$}\DisplayProof$ \\ \hline
Disjunction & 
$\RightLabel{\scriptsize{$\lor$ L  $\phi \lor \psi$}}\AxiomC{$\Gamma, \phi \vdash \Delta$}\AxiomC{$\Gamma, \psi \vdash \Delta$}\BinaryInfC{$\Gamma, \phi \lor \psi \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\lor$ R  $\phi \lor \psi$}}\AxiomC{$\Gamma \vdash \phi, \Delta$}\UnaryInfC{$\Gamma \vdash \phi \lor \psi, \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\lor$ R  $\phi \lor \psi$}}\AxiomC{$\Gamma \vdash \psi, \Delta$}\UnaryInfC{$\Gamma \vdash \phi \lor \psi, \Delta$}\DisplayProof$ \\ \hline
Implication & 
$\RightLabel{\scriptsize{$\to$ L  $\phi \to \psi$}}\AxiomC{$\Gamma \vdash \phi, \Delta$}\AxiomC{$\Gamma, \psi \vdash \Delta$}\BinaryInfC{$\Gamma, \phi \to \psi \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\to$ R  $\phi \to \psi$}}\AxiomC{$\Gamma, \phi \vdash \psi, \Delta$}\UnaryInfC{$\Gamma \vdash \phi \to \psi, \Delta$}\DisplayProof$ \\ \hline
Quantifiers & 
$\RightLabel{\scriptsize{$\forall$ L $\forall x \phi(x)$}}\AxiomC{$\Gamma, \phi(t) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \phi(x) \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\forall$ R $\forall x \phi(x)$}}\AxiomC{$\Gamma \vdash \phi(y), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \phi(x), \Delta$}\DisplayProof$ \\ 
& 
$\RightLabel{\scriptsize{$\exists$ L $\exists x \phi(x)$}}\AxiomC{$\Gamma, \phi(y) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \phi(x) \vdash \Delta$}\DisplayProof$ \quad
$\RightLabel{\scriptsize{$\exists$ R $\exists x \phi(x)$}}\AxiomC{$\Gamma \vdash \phi(t), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \phi(x), \Delta$}\DisplayProof$ \\ \hline
\end{tabular}
\end{table}



\section{Translation}
\begin{definition} \textbf{node translating function $\mathcal{T}$}
Given a signed sentence list L with sentences
 $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
and 
    $ \{F_{q_1}\delta{i}, F_{q_2}\delta{i+1}...\}$ and a $w \in \{p_1,p_2,...\} \cup \{q_1,q_2,...\}$ 
then: \\  $ \mathcal{T} (L,w$) = $\Gamma_{1}, \Gamma_{2}, ... \vdash \Delta_1, \Delta_2, ...$, were: \\
$\{ T_{q_1}\Gamma_{1}, T_{q_2}\Gamma_{2} , ...\}$    are the elements of $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$ such that  $p \geq w$ 
and 
$\{ F_{q_1}\Delta_{1}, F_{q_2}\Delta_{2} , ...\}$ are the elements of $\{ F_{q_1}\delta_{1}, F_{q_2}\delta_{2}, ...\}$ such that  $q \leq w$ 

\end{definition}


\begin{theorem}
    Given signed sentence list $L$ and a $w$,  
    if L is intuitionistically valid then the sequent $\mathcal{T}(L, w)$ is not intuitionistically valid.
\end{theorem}

    \begin{proof} 
    If L has the sentences
    $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
   and 
       $ \{F_{q_1}\delta{i}, F_{q_2}\delta{i+1}...\}$ 
    , that signifies an assumption of existance of a frame $ \mathcal{C}$
    such that: 


    $ \mathcal{C}(p_1) \Vdash \gamma_{1}$ and $ \mathcal{C}(p_{2}) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(q_{1}) \nvDash \delta_{1}$  and $ \mathcal{C}(q_{2}) \nvDash \delta_{2}$ 
   \\  which implicitly means, by the definition of extension: 
    
   ($ \mathcal{C}(p) \Vdash \gamma_{1}$ for all $p \geq p_1$) and ($ \mathcal{C}(p) \Vdash \gamma_{2}$ for all $p \geq p_2$) and ... ($ \mathcal{C}(p) \nvDash \delta_{1}$ for all $p \leq q_{1}$) and ($ \mathcal{C}(p) \nvDash \delta_{2}$ for all $p \leq q_{2}$)...
     
   
   Take the structure $\mathcal{C}(w)$ inside of $\mathcal{C}$. We can infer:
   
   $ \mathcal{C}(w) \Vdash \Gamma_{1}$ and $ \mathcal{C}(w) \Vdash \Gamma_{2}$ and ... $ \mathcal{C}(w) \nvDash \Delta_1$  and $ \mathcal{C}(w) \nvDash \Delta_2 ...$.
   
   $\mathcal{C}(w)$ is a counterexample proving the non-validity of 
    $\Gamma_{1}, \Gamma_{2}, ... \vdash \Delta_1, \Delta_2, ...$
    \end{proof}
\subsection{Classical Translation}

\begin{theorem} 
    L is valid if and only if $\mathcal{T}(L,\emptyset)$ is not valid 
\end{theorem}

\begin{proof}
    It goes directly from the definiton:
    \begin{itemize}
\item If the signed sentence list is valid, then the sequent is invalid by corolary of [TODO]
\item If the signed sentence list is not valid, it does not exist a counterexample for $\mathcal{T}$(L). (Note that 
we can not say the same for the intuitionistic case)
   \end{itemize}
\end{proof}



\begin{theorem}
     Given a signed sentence list l with $\sigma \in l$ , then 
    $\RightLabel{rule}\AxiomC{$\mathcal{T}( f(\sigma,l))$}\UnaryInfC{$\mathcal{T}(l)$}\DisplayProof$ 
    is a valid rule.

\end{theorem}

\begin{proof}
    Here will show the implicit quantifier rule being used:\\ 
    if $L-\sigma$ has sentences $\{ T\Gamma_{1}, T\Gamma_{2}, ...\}$ and  $ \{F\Delta_1, F\Delta_2 ...\} $, then: 
    \small{
    \begin {itemize}

    \item
    $\AxiomC{$\mathcal{T}( f(T\neg \alpha,l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
    $=\AxiomC{$\mathcal{T}( (L-T\neg \alpha)||T \neg \alpha||F \alpha)$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
    $=\AxiomC{$\Gamma ,\neg \alpha \vdash \alpha, \Delta$}\UnaryInfC{$\Gamma, \neg \alpha \vdash \Delta$}\DisplayProof$ 
    $=\RightLabel{\scriptsize{$\neg$R}}\AxiomC{$\Gamma ,\neg \alpha \vdash \alpha, \Delta$}\UnaryInfC{$\Gamma, \neg \alpha , \neg \alpha \vdash \Delta$}\UnaryInfC{$\Gamma, \neg \alpha \vdash \Delta$}\DisplayProof$ 
    \item 
    $\AxiomC{$\mathcal{T}( f(F\neg \alpha,l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
    $=\AxiomC{$\mathcal{T}( (L-F\neg \alpha)||F \neg \alpha||T \alpha)$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
    $=\AxiomC{$\Gamma ,\neg \alpha \vdash \neg \alpha, \Delta$}\UnaryInfC{$\Gamma \vdash , \neg \alpha \Delta$}\DisplayProof$ 
    $=\RightLabel{\scriptsize{$\neg$L}}\AxiomC{$\Gamma , \alpha \vdash \neg \alpha, \Delta$}\UnaryInfC{$\Gamma \vdash \neg \alpha , \neg \alpha \Delta$}\UnaryInfC{$\Gamma,  \vdash  \neg \alpha \Delta$}\DisplayProof$ 
    \item 
    $\AxiomC{$\mathcal{T}( f(T(\alpha \land \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
    $=\AxiomC{$\mathcal{T}( (L-T(\alpha \land \beta))||\alpha \land \beta||T \alpha||T \beta)$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
    $=\AxiomC{$\Gamma ,\alpha, \beta, \alpha \land \beta \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \land \beta \vdash \Delta$}\DisplayProof$ 
    $=\RightLabel{\scriptsize{$\land$L}}\AxiomC{$\Gamma ,\alpha, \beta \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha, \beta, \alpha \land \beta \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \land \beta \vdash \Delta$}\DisplayProof$
    \item 
    $\AxiomC{$\mathcal{T}( f(F(\alpha \land \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
    $=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || F \alpha) $}\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || F \beta) $}\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$
    $=\AxiomC{$\Gamma ,\alpha, \alpha \land \beta \vdash \Delta$}\AxiomC{$\Gamma , \beta, \alpha \land \beta \vdash \Delta$}\BinaryInfC{$\Gamma,\vdash  \alpha \land \beta  ,\Delta$}\DisplayProof$
    $=\RightLabel{\scriptsize{$\land$R}}\AxiomC{$\Gamma ,\alpha, \alpha \land \beta \vdash \Delta$}\AxiomC{$\Gamma , \beta, \alpha \land \beta \vdash \Delta$}\BinaryInfC{$\Gamma \vdash  \alpha \land \beta ,\alpha \land \beta, \Delta$}\UnaryInfC{$\Gamma,\vdash  \alpha \land \beta  ,\Delta$}\DisplayProof$
    \item 
$\AxiomC{$\mathcal{T}( f(T(\alpha \lor \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || T \alpha)$}\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || T \beta)$}\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$
$=\AxiomC{$\Gamma ,\alpha , \alpha \lor \beta \vdash \Delta$}\AxiomC{$\Gamma ,\beta, \alpha \lor \beta \vdash \Delta$}\BinaryInfC{$\Gamma, \alpha \lor \beta \vdash \Delta$}\DisplayProof$
$=\RightLabel{\scriptsize{$\lor$L}} \AxiomC{$\Gamma ,\alpha \vdash  \alpha \lor \beta,\Delta$}\AxiomC{$\Gamma , \beta, \alpha \lor \beta \vdash \Delta$}\BinaryInfC{$\Gamma \vdash  \alpha \lor \beta,\alpha \lor \beta ,\Delta$}\UnaryInfC{$\Gamma \vdash  \alpha \lor \beta ,\Delta$}\DisplayProof$
\item 
$\AxiomC{$\mathcal{T}( f(F(\alpha \lor \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
$=\AxiomC{$\mathcal{T}( (L-F(\alpha \lor \beta))||F \alpha||F \beta)$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
$=\AxiomC{$\Gamma \vdash \alpha \lor \beta,\alpha,\beta,\Delta$}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$
$=\RightLabel{\scriptsize{$\land$R}}\AxiomC{$\Gamma \vdash \alpha \lor \beta,\alpha,\beta,\Delta$}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta,\alpha \lor \beta,\alpha,\beta,\Delta$}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$
\item 

$\AxiomC{$\mathcal{T}( f(T(\alpha \rightarrow \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || F \alpha )$}\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || T \beta ) $}\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma, \alpha, \alpha \rightarrow \beta \vdash \Delta$}\AxiomC{$\Gamma, \alpha \rightarrow \beta \vdash  \beta, \Delta$}\BinaryInfC{$\Gamma, \alpha \rightarrow \beta \vdash \Delta$}\DisplayProof$  
$=\RightLabel{\scriptsize{$\rightarrow$L}}\AxiomC{$\Gamma, \alpha, \alpha \rightarrow \beta \vdash \Delta$}\AxiomC{$\Gamma, \alpha \rightarrow \beta \vdash  \beta, \Delta$}\BinaryInfC{$\Gamma, \alpha \rightarrow \beta,\alpha \rightarrow \beta  \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha \rightarrow \beta \vdash \Delta$}\DisplayProof$  

\item 
$\AxiomC{$\mathcal{T}( f(F(\alpha \rightarrow \beta),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}((L - F(\alpha \rightarrow \beta)) || F(\alpha \rightarrow \beta) || T \alpha || F \beta)$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma , \alpha \vdash \beta, \alpha \rightarrow \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \Delta$}\DisplayProof$
$=\RightLabel{\scriptsize{$\rightarrow$R}}\AxiomC{$\Gamma , \alpha \vdash \beta, \alpha \rightarrow \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \alpha \rightarrow \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \Delta$}\DisplayProof$

\item 
$\AxiomC{$\mathcal{T}( f(T(\forall x \, \phi(x)),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || T \phi(c_i) )$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma, \forall x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \, \phi(x) \vdash \Delta$}\DisplayProof$  
$=\RightLabel{\scriptsize{$\forall$L}}\AxiomC{$\Gamma, \forall x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \, \phi(x), \forall x \, \phi(x) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \, \phi(x) \vdash \Delta$}\DisplayProof$

and $c_i$ does not occour in $\Gamma$ or $\Delta$, as it is a new one.
\item 
$\AxiomC{$\mathcal{T}( f(F(\forall x \, \phi(x)),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || F \phi(c_i) )$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma \vdash \phi(c_i), \forall x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \Delta$}\DisplayProof$  
$=\RightLabel{\scriptsize{$\forall$R}}\AxiomC{$\Gamma \vdash \phi(c_i), \forall x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \forall x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \Delta$}\DisplayProof$

\item 
$\AxiomC{$\mathcal{T}( f(T(\exists x \, \phi(x)),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || T \phi(c_i) )$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma, \exists x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \, \phi(x) \vdash \Delta$}\DisplayProof$  
$=\RightLabel{\scriptsize{$\exists$L}}\AxiomC{$\Gamma, \exists x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \, \phi(x), \exists x \, \phi(x) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \, \phi(x) \vdash \Delta$}\DisplayProof$

and $c_i$ does not occour in $\Gamma$ or $\Delta$, as it is a new one.
\item 
$\AxiomC{$\mathcal{T}( f(F(\exists x \, \phi(x)),l))$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\mathcal{T}( L - \sigma|| \sigma || F \phi(c_i) )$}\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
$=\AxiomC{$\Gamma \vdash \phi(c_i), \exists x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \Delta$}\DisplayProof$  
$=\RightLabel{\scriptsize{$\exists$R}}\AxiomC{$\Gamma \vdash \phi(c_i), \exists x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \exists x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \Delta$}\DisplayProof$

\end  {itemize}
}
    

\end{proof}


\begin{definition} \textbf{Translation in classical logic}
    given a tableaux proof tree development and its root r $\tau$, we define $\mathcal{T}_p(\tau)$:
    \begin{itemize}
        \item if $\tau$ = r and there are $T \sigma $ and $F \sigma $ on r:\\$\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Ax $\sigma$}}\AxiomC{}\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$
        \item if $\tau$ = r and there is no $\sigma$ such that $T \sigma $ and $F \sigma $ are on r: \\ $\mathcal{T}_p(\tau) = \mathcal{T}(\tau) $

        \item if $r$ has a single child $r_0$ with a corresponding subtree $\tau_0$: \\by definition the last theorem exits a sentence $\sigma$ such that  
        $f(\sigma,r)=f_{Rule}(\sigma,r)=r_0=r_0$, and so  $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on  $\sigma$}}\AxiomC{$\mathcal{T}_p(\tau_0)$}\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$
        \item if $r$ has two children $r_1$ and $r_2$ with corresponding subtrees $\tau_1$ and $\tau_2$:\\ by the last theorem there exists a sentence $\sigma$  such that
            $f(\sigma, r) = f_{Rule}(\sigma, r) = \{r_1, r_2\}$, and so  
            $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on $\sigma$}}\AxiomC{$\mathcal{T}_p(\tau_1)$}\AxiomC{$\mathcal{T}_p(\tau_2)$}\BinaryInfC{$\mathcal{T}(r)$}\DisplayProof$
    \end{itemize}
\end{definition}





\subsection{Intuitionistic Translation}





%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

    \bibitem{book1}
    Nerode, A., Shore, R.A.: Logic for Applications. 2nd edn. Texts in Computer Science. Springer, New York, NY (1997). \doi{10.1007/978-1-4612-0649-1}
    
    \bibitem{book2}
    Dummett, M.: Elements of Intuitionism. Oxford Logic Guides. Clarendon Press (2000). \url{https://books.google.fr/books?id=JVFzknbGBVAC}
        \bibitem{kripke1965}
    Kripke, S.A.: Semantical analysis of intuitionistic logic I. In: Studies in Logic and the Foundations of Mathematics. Elsevier (1965)


    \bibitem{book3}
    Svejdar, V.: On Sequent Calculi for Intuitionistic Propositional Logic. CMUC (2005). \url{https://www.muni.cz/en/research/publications/1234567}

\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)


\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.coBm/lncs}, last accessed 2023/10/25
\end{thebibliography}
\end{document}
