
\def\structureDefinition{
\begin{definition}
    \textbf{A Structure of a Language} (an \(\mathcal{L}\)-structure) is a triple that consists of a domain and two assignments:
    \begin{itemize}
        \item An assignment from the constant symbols of the language to the domain.
        \item An assignment from the predicate symbols of the language to predicates in the domain.
    \end{itemize}
    Here the domain is the finite set of the objects being described by the language. 
\end{definition}
}

\def\kripkeFrameDefinition{
\begin{definition}
    \textbf{A Kripke Frame} of a Language \(\mathcal{L}\), \(\mathcal{C} = (R, \{C(p)\}_{p \in R})\) consists of a partially ordered set \(R\), and an \(\mathcal{L}\)-structure \(C(p)\) for all \(p\)'s in \(R\). 
    Furthermore, in a Kripke Frame, if \(p \leq q\), then \(C(q)\) extends \(C(p)\) in the following sense:
    \begin{itemize}
        \item All sentences that are true in \(C(p)\) are true in \(C(q)\).
        \item The domain of \(C(p)\) is included in the domain of \(C(q)\).
        \item The assignments in \(C(p)\) are the same as in \(C(q)\) for the domain of \(C(p)\)
    \end{itemize}
\end{definition}
}

\def\forcingDefinition{
\begin{definition}
    \textbf{Forcing}. When a sentence \(\phi\) of a language \(\mathcal{L}\) is \textbf{forced} by a structure \(C(p)\) of a \(\mathcal{L}\)-frame \(\mathcal{C}\), we denote it as:
    \(p \Vdash_{\mathcal{C}} \phi\) \\
    Forcing is defined by induction: \cite{book1}
    
    \begin{itemize}
        \item \(p \Vdash_{\mathcal{C}} \phi \text{ iff } \phi \text{ is true in } C(p)\) (if \(\phi\) is an atomic sentence).
        \item \(p \Vdash_{\mathcal{C}} (\phi \to \psi) \text{ iff }\) for all \(q \geq p\), if \(q \Vdash_{\mathcal{C}} \phi\), then \(q \Vdash_{\mathcal{C}} \psi\).
        \item \(p \Vdash_{\mathcal{C}} \neg \phi \text{ iff } \) for all \(q \geq p\), \(q\) does not force \(\phi\).
        \item \(p \Vdash_{\mathcal{C}} (\forall x) \phi(x) \text{ iff }\) for all \(q \geq p\) and \(d\) in \(\mathcal{L}_{C(q)}\), \(q \Vdash_{\mathcal{C}} \phi(d)\).
        \item \(p \Vdash_{\mathcal{C}} (\exists x) \phi(x) \text{ iff }\) there exists a \(d\) in \(\mathcal{L}_{C(q)}\), such that \(p \Vdash_{\mathcal{C}} \phi(d)\).
        \item \(p \Vdash_{\mathcal{C}} (\phi \land \psi) \text{ iff } p \Vdash_{\mathcal{C}} \phi \text{ and } p \Vdash_{\mathcal{C}} \psi\).
        \item \(p \Vdash_{\mathcal{C}} (\phi \lor \psi) \text{ iff } p \Vdash_{\mathcal{C}} \phi \text{ or } p \Vdash_{\mathcal{C}} \psi\).
    \end{itemize}
\end{definition}
}

\def\intuitionisticValidityDefinition{
\begin{definition}
    \textbf{Intuitionistic Validity}. A sentence of a language \(\mathcal{L}\) is Intuitionistically valid if it is forced in all structures of all Kripke frames of \(\mathcal{L}\).
\end{definition}
}

\def\classicalValidityDefinition{
\begin{definition}
    \textbf{Classical Validity}. A sentence of a language \(\mathcal{L}\) is classically valid if it is forced by all singleton structure Kripke frames of \(\mathcal{L}\).
\end{definition}
}

\def\signedSentenceIntuitionisticDefinition{
\begin{definition}
    \textbf{A Signed Sentence} is a forcing assertion inside of a tableaux proof. It has the format $T_{q} \phi $ or $F_{p} \phi $ \\
    \textbf{A Signed Sentence List} is a list of forcing assertions inside of a tableaux proof. We say that a list of forcing assertions $L$ made out of  sentences $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
  and $ \{F_{q_1}\delta_{1}, F_{q_2}\delta_{2}...\} $
     is intuitionistically valid if there exists a frame $\mathcal{C}$ that respects L : 
     
     $ \mathcal{C}(p_1) \Vdash \gamma_{1}$ and $ \mathcal{C}(p_{2}) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(q_{1}) \nvDash \delta_{1}$  and $ \mathcal{C}(q_{2}) \nvDash \delta_{2}$
\end{definition}
}

\def\fIntuitionisticDefinition{
\begin{definition}
    The function $f$ takes a signed sentence $\sigma$ and a signed sentence list $L$ and returns one or two signed sentence lists.  \\$f(\sigma,L)$ is defined as follows:
    \\(here we denote $l:l'$ = $l_1,l_2...,l_{|l|}, l'_1,l'_2..,l'_{|l'|} $)
    \\if $\sigma \in L$:
        \begin{itemize}
            \item $f(T_{p}\alpha  ,L) = [L - \sigma: \sigma : F_{p'}\alpha] $ \\for a  $p' \geq p$ such that $T_{p'}\alpha$ not present in $L$. ($\alpha$ is atomic)
            \item $f(T_{p} \neg \alpha,L) = [L - \sigma: \sigma : F_{p'}\alpha] $ \\for a  $p' \geq p$ such that $T_{p'} ,L$ not present in $L$.
            \item $f(F_{p} \neg \alpha,L) = [L - \sigma : \sigma : T_p' \alpha]$  \\for a new $p' \geq p$ 
            \item $f(T_{p} (\alpha \land \beta), L) = [L - \sigma: \sigma : T_{p} \alpha : T_{p} \beta]$.
            \item $f(F_{p} (\alpha \land \beta), L) = [L - \sigma: \sigma : F_{p} \alpha],[ L - \sigma: \sigma : F_{p} \beta]$.
            \item $f(T_{p} (\alpha \lor \beta), L) = [L - \sigma: \sigma : T_{p} \alpha],[ L - \sigma: \sigma : T_{p} \beta]$.
            \item $f(F_{p} (\alpha \lor \beta), L) = [L - \sigma: \sigma : F_{p} \alpha : F_{p} \beta]$.
            \item $f(T_{p} (\alpha \to \beta), L) = [L - \sigma: \sigma : F_{p'} \alpha],[ L - \sigma : \sigma : T_{p'} \beta]$ \\for a new $p' \geq p$ 
            \item $f(F_{p} (\alpha \to \beta), L) = [L - \sigma: \sigma : T_{p'} \alpha : F_{p'} \beta]$ \\for a  $p' \geq p$ present in $\sigma:L$ and such that $T_{p'} (\alpha)$ and $F_{p'} (\beta)$ not  $L$.
            \item $f(T_{p} (\forall x) \phi(x), L) = [L - \sigma: \sigma : T_{p} \phi(c_i) ]$\\ for the first constant $c_i$ such that $T_{p} \phi(c_i)$ is not in $L$.
            \item $f(F_{p'} (\forall x) \phi(x), L) = [L - \sigma: \sigma : F_{p} \phi(c_i) ]$\\ for the first constant $c_i$ not present in $\sigma:L$ and a new $p' \geq p$
            \item $f(T_{p'} (\exists x) \phi(x), L) = [L - \sigma: \sigma : T_{p} \phi(c_i) ]$ \\for the first constant $c_i$ not present in $\sigma:L$ and a new $p' \geq p$.
            \item $f(F_{p} (\exists x) \phi(x), L) = [L - \sigma: \sigma : F_{p} \phi(c_i) ]$\\ for the first constant $c_i$ such that $F_{p} \phi(c_i)$ is not in $L$ and .
        \end{itemize} 
    if $\sigma \notin L$:
    \begin{itemize}
         \item $f(\sigma,L) = L $
    \end{itemize}
\end{definition}
}


\def\wellBehavedTheorem{
    \begin{theorem}
        Given a signed sentence list L, if L is intuitionistically valid then f(L) is intuitionistically valid 
    \end{theorem}
    \begin{proof}
        \cite{book1} proves this by using the definition of forcing. We will do the most complex case, that has the most part of the ideas needed for the other ones:
        

        Case: if $L \ni F_{p} (\forall x) \phi(x) $ is intuitionistically valid, then there exists a frame $\mathcal{C}$ that respects it (in the sense of the Definition 6). 
        $\mathcal{C}$ contains q and a c $\in \mathcal{C}(q)$ such that $\mathcal{C}(c) \nVdash \phi(c)$. Let  $\mathcal{C'}$ be the same
        as $\mathcal{C}$, with the new world $\mathcal{C}(p')$ such that $\mathcal{C}(p') := \mathcal{C}(q)$ and $c_i := c$

        In other words, let  $\mathcal{C'}$ be a frame that is exactly like $\mathcal{C}$ with addition of a new structure $p' \geq p$ such that $\mathcal{C}'(p') \nVdash \phi(c_i)$ for a new $c_i$. We know that 
        $\mathcal{C}'$ exists by the definition of forcing for $\forall$ in C. Also $\mathcal{C}'$ is a frame that respects
        $f(\forall x \phi(x), L) = [L - \forall x \phi(x): \forall x \phi(x) : T_{p} \phi(c_i) ]$. 
    \end{proof}
}

\def\TableauxDevelopmentDefinition{
    \begin{definition}
        \textbf{The tableaux Development of a Sentence } is defined inductivelly: 
        \begin{itemize}
            \item A tree with the single node $F_{\emptyset}\phi$ is a tableaux development of $\phi$. 
            \item If $\tau$ is a tableaux development of $\phi$, then $\hookleftarrow(\sigma,\tau)$ is a tableaux development of $\phi$. Where:
        \end{itemize}
    
        $\hookleftarrow(\sigma,\tau) = $ $\tau$ with $f(\sigma, l) $added to all leaves l that contain $\sigma$
    \end{definition}
}

\def\TableauxDevelopmentListDefinition{
    \begin{definition}
        \textbf{The tableaux Development of a List of Sentences } is defined inductively: 
        \begin{itemize}
            \item A tree with the single node $L$ is a tableaux development of $L$. 
            \item If $\tau$ is a tableaux development of $L$, then $\hookleftarrow(\sigma,\tau)$ is a tableaux development of $L$. Where:
        \end{itemize}
    
        $\hookleftarrow(\sigma,\tau) = $ the extension of $\tau$ with $f(\sigma, l) $added to all leaves l that contain $\sigma$
    \end{definition}
}



\def\soundnessTheorem {
\begin{theorem} 
    The following implication is true: \\ 
    If L is intuitionistically valid then one of the leaves of $ \hookleftarrow (\sigma_n,\hookleftarrow(\sigma_{n-1}(.....(\hookleftarrow(\sigma_1 ,L )...)))) $ is intuitionistically valid.
\end{theorem}

\begin{proof}
    If L is intuitionistically invalid, the premise is false and the implication holds. 
    If L is intuitionistically valid,
    The proof goes by induction on the number of times $\hookleftarrow$ is applied :


            The base case is true by definition: L is a intuitionistically valid leaf. 
            Next we assume $\tau' = \hookleftarrow (\sigma, \tau)$.
            By the induction hypothesis, there exists an intuitionistically valid leaf $\sigma$ in $\tau$.
                \begin{itemize}
                    \item If $\sigma$ is a leaf in $\tau$, then  the theorem holds for $\tau'$.
                    \item If $\sigma$ is not a leaf in $\tau$, then:
                         One or two nodes were added to $\sigma$ in $\tau'$ by the definition of $\hookleftarrow$.
                         By the theorem 1, one of the added nodes is also intuitionistically valid.
                         Consequently, the theorem holds for $\tau'$.
                \end{itemize}
\end{proof}

}

\def\completeiteratordefinition{
\begin{definition}
    $\hookleftarrow_c(\tau) = \tau$ with $f(h,l)$ added to all leaves l that contain $\sigma$.
     h is the first signed sentence of the shallowest (and after that leftmost) non-contradictory leaf. 
     here, c stands for complete. A contradictory leaf is a leaf that has T and F of the same sentence.
\end{definition}
}


\def\signedSentenceClassicalDefinition{

\begin{definition}
    \textbf{A Signed Sentence} is a forcing assertion inside of a tableaux proof. It can have the format $T \phi $ or $F \phi $ \\
    \textbf{A Signed Sentence List} is a list of forcing assertions inside of a tableaux proof. We say that a list of forcing assertions $L$ made out of sentences $\{ T\gamma_{1}, T\gamma_{2}, ...\}$
  and $ \{F\delta_{1}, F\delta_{2}...\} $
     is "classically valid" if there exists a single-structure frame  $\mathcal{C}$ such that $ \mathcal{C}(\emptyset) \Vdash \gamma_{1}$ and $ \mathcal{C}(\emptyset) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(\emptyset) \nVdash \delta_{1}$  and $ \mathcal{C}(\emptyset) \nVdash \delta_{2}$
\end{definition}
 
}

\def\fClassicalDefinition{
    \begin{definition}
        The function $f$ takes a signed sentence $\sigma$ and a signed sentence list $L$ and returns one or two signed sentence lists.  \\$f(\sigma,L)$ is defined as follows:
        \\(here we denote $l:l'$ = $l_1,l_2...,l_{|l|}, l'_1,l'_2..,l'_{|l'|} $)
        \\if $\sigma \in L$:
            \begin{itemize}
                \item $f(T \neg \alpha,L) = [L - \sigma: \sigma : F \alpha]$.
                \item $f(F \neg \alpha,L) = [L - \sigma : \sigma : T \alpha]$.
                \item $f(T (\alpha \land \beta), L) = [L - \sigma: \sigma : T \alpha : T \beta]$.
                \item $f(F (\alpha \land \beta), L) = [L - \sigma: \sigma : F \alpha],[ L : \sigma : F \beta]$.
                \item $f(T (\alpha \lor \beta), L) = [L - \sigma: \sigma : T \alpha],[ L : \sigma : T \beta]$.
                \item $f(F (\alpha \lor \beta), L) = [L - \sigma: \sigma : F \alpha : F \beta]$.
                \item $f(T (\alpha \to \beta), L) = [L - \sigma: \sigma : F \alpha],[ L : \sigma : T \beta]$.
                \item $f(F (\alpha \to \beta), L) = [L - \sigma: \sigma : T \alpha : F \beta]$.
                \item $f(T (\forall x) \phi(x), L) = [L - \sigma: \sigma : T \phi(c_i)]$ \\ for the first constant $c_i$ such that $T \phi(c_i)$ is not in $L$.
                \item $f(F (\forall x) \phi(x), L) = [L - \sigma: \sigma : F \phi(c_i)]$ \\ for the first constant $c_i$ not present in $L$.
                \item $f(T (\exists x) \phi(x), L) = [L - \sigma: \sigma : T \phi(c_i)]$ \\ for the first constant $c_i$ not present in $L$.
                \item $f(F (\exists x) \phi(x), L) = [L - \sigma: \sigma : F \phi(c_i)]$ \\ for the first constant $c_i$ such that $F \phi(c_i)$ is not in $L$.
            \end{itemize}  
        if $\sigma \notin L$:
        \begin{itemize}
             \item $f(\sigma,L) = L $
        \end{itemize}
    \end{definition}
}


\def\sequentDefinition{    
\begin {definition}
    \textbf{A Sequent}  is an expression of the form 
    \[
    \Gamma \vdash \Delta
    \]
    where $\Gamma = \{\Gamma_1, \Gamma_2, \Gamma_3,...\}$ and $\Delta = \{\Delta_1,\Delta_2,\Delta_3 ...\}$
     are  finite sets of formulas. $\Gamma $ is called the antecedent, and 
    $\Delta$ is called the succedent. 
\end {definition}
}

\def\sequentProofDefinition{    
\begin {definition}
    \textbf{Sequent} A sequent is an expression of the form 
    \[
    \Gamma \vdash \Delta
    \]
    where $\Gamma = \{\Gamma_1, \Gamma_2, \Gamma_3,...\}$ and $\Delta = \{\Delta_1,\Delta_2,\Delta_3 ...\}$
     are  finite sets of formulas. 
     
\end {definition}
}




\def\sequentValidityDefinition{
    \begin {definition} \textbf{(Intuitionistic Validity of a Sequent)}
A sequent is intuitionistically valid if for all Kripke frames, if all of $\Gamma$ are forced, then at least one of $\Delta$ is forced.
\end {definition}

}






\def\developmentSequentClassicalDefinition{

\begin {definition}
    A single sequent is a classical sequent proof-tree development\\
    Any of the rules of the table 1 applied to a classical sequent proof-tree development is a sequent proof-tree development\\
    A classical sequent proof-tree is  a classical sequent proof-tree development with axioms on all leaves.
\end {definition} 

}


\def\developmentSequentIntuitionisticDefinition{

\begin {definition}
    A single sequent is an intuitionistic sequent proof-tree development\\
    Any of the rules of table 2 applied to an intuitionistic sequent proof-tree development is an intuitionistic sequent proof-tree development\\
    A intuitionistic squent proof-tree is  a intuitionistic sequent proof-tree development with axioms on all leafs.
\end {definition} 

}




\def\nodeTranslationFunction{
    \begin{definition} \textbf{Node-Translating Function $\mathcal{T}$}


        Given a signed sentence list L with sentences
         $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
        and 
            $ \{F_{q_1}\delta_{1}, F_{q_2}\delta_{2}...\}$ and a frame $w \in \{p_1,p_2,...\} \cup \{q_1,q_2,...\}$ 
        then: \\  $ \mathcal{T} (L,w$) = $\Gamma_{1}, \Gamma_{2}, ... \vdash \Delta_1, \Delta_2, ...$, where: \\
        $\{ T_{p'_1}\Gamma_{1}, T_{p'_2}\Gamma_{2} , ...\}$    are the elements of $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$ such that  $p' \leq w$ 
        and 
        $\{ F_{q'_1}\Delta_{1}, F_{q'_2}\Delta_{2} , ...\}$ are the elements of $\{ F_{q_1}\delta_{1}, F_{q_2}\delta_{2}, ...\}$ such that  $q' \geq w$ 
        

        For the classical case: $ \mathcal{T} (L) = \mathcal{T} (L,\emptyset) $
        \end{definition}
}


\def\nodeTranslationFunction{
    \begin{definition} \textbf{Node Translating Function $\mathcal{T}$}


        Given a signed sentence list L with sentences
         $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
        and 
            $ \{F_{q_1}\delta_{1}, F_{q_2}\delta_{2}...\}$ and a frame $w \in \{p_1,p_2,...\} \cup \{q_1,q_2,...\}$ 
        then: \\  $ \mathcal{T} (L,w$) = $\Gamma_{1}, \Gamma_{2}, ... \vdash \Delta_1, \Delta_2, ...$, where: \\
        $\{ T_{p'_1}\Gamma_{1}, T_{p'_2}\Gamma_{2} , ...\}$    are the elements of $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$ such that  $p' \leq w$ 
        and 
        $\{ F_{q'_1}\Delta_{1}, F_{q'_2}\Delta_{2} , ...\}$ are the elements of $\{ F_{q_1}\delta_{1}, F_{q_2}\delta_{2}, ...\}$ such that  $q' \geq w$ 
        

        For the classical case: $ \mathcal{T} (L) = \mathcal{T} (L,\emptyset) $
        \end{definition}
}


\def\uselessTheorem{
    \begin{theorem}
        Given signed sentence list $L$ and a $w$,  
        if L is intuitionistically valid then the sequent $\mathcal{T}(L, w)$ is not intuitionistically valid.
    \end{theorem}
    
        \begin{proof} 
        If L has the sentences
        $\{ T_{p_1}\gamma_{1}, T_{p_2}\gamma_{2}, ...\}$
       and 
           $ \{F_{q_1}\delta_{1}, F_{q_2}\delta_{2}...\}$ ,it exists a frame $ \mathcal{C}$ such that: 
    
    
        $ \mathcal{C}(p_1) \Vdash \gamma_{1}$ and $ \mathcal{C}(p_{2}) \Vdash \gamma_{2}$ and ... $ \mathcal{C}(q_{1}) \nvDash \delta_{1}$  and $ \mathcal{C}(q_{2}) \nvDash \delta_{2}$ 
       \\  which implicitly entails, by the definition of extension in frames: 
        
       ($ \mathcal{C}(p) \Vdash \gamma_{1}$ for all $p \geq p_1$) and ($ \mathcal{C}(p) \Vdash \gamma_{2}$ for all $p \geq p_2$) and ... ($ \mathcal{C}(p) \nvDash \delta_{1}$ for all $p \leq q_{1}$) and ($ \mathcal{C}(p) \nvDash \delta_{2}$ for all $p \leq q_{2}$)...
         
       
       Take the structure $\mathcal{C}(w)$ inside of $\mathcal{C}$. We can infer:
       
       $ \mathcal{C}(w) \Vdash \Gamma_{1}$ and $ \mathcal{C}(w) \Vdash \Gamma_{2}$ and ... $ \mathcal{C}(w) \nvDash \Delta_1$  and $ \mathcal{C}(w) \nvDash \Delta_2 ...$.
       
       $\mathcal{C}$ is thus a counterexample proving the non-validity of 
        $\Gamma_{1}, \Gamma_{2}, ... \vdash \Delta_1, \Delta_2, ...$
        \end{proof}
}

\def\otheruselesstheorem{
    \begin{theorem} 
        L is valid if and only if $\mathcal{T}(L,\emptyset)$ is not valid 
    \end{theorem}
    
    \begin{proof}
        It goes directly from the definition:
        \begin{itemize}
    \item If the signed sentence list is valid, then the sequent is invalid by corollary of [TODO]
    \item If the signed sentence list is not valid, it does not exist a counterexample for $\mathcal{T}$(L). (Note that 
    we can not say the same for the intuitionistic case)
       \end{itemize}
    \end{proof}
}

\def\localTranslationValidityTheorem{
    \begin{theorem}
        $\RightLabel{}\AxiomC{$\mathcal{T}( f(\sigma,L))$}\doubleLine\UnaryInfC{$\mathcal{T}(l)$}\DisplayProof$ 
       is classically admissible
   
   \end{theorem}
   
   \begin{proof}
       Here will show the implicit contraction rule being used:\\ 
       If $L-\sigma$ has sentences $\{ T\Gamma_{1}, T\Gamma_{2}, ...\}$ and  $ \{F\Delta_1, F\Delta_2 ...\} $ , $\Gamma =  \Gamma_{1}, \Gamma_{2}$, ... and $\Delta = \Delta_{1}, \Delta_{2}, $... then: 
       \small{
       \begin {itemize}
       \renewcommand{\arraystretch}{4}
    \item If  $f = f_{T\neg}$:\\
    \begin{tabular}{lll}
    
     $\AxiomC{$\mathcal{T}( f(T\neg \alpha,L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
     & $=\AxiomC{$\mathcal{T}( (L-T\neg \alpha):T \neg \alpha:F \alpha)$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ \\ 
     & $=\AxiomC{$\Gamma ,\neg \alpha \vdash \alpha, \Delta$}\doubleLine\UnaryInfC{$\Gamma, \neg \alpha \vdash \Delta$}\DisplayProof$ 
      $=\RightLabel{\scriptsize{$\neg$R}}\AxiomC{$\Gamma ,\neg \alpha \vdash \alpha, \Delta$}\UnaryInfC{$\Gamma, \neg \alpha , \neg \alpha \vdash \Delta$}\UnaryInfC{$\Gamma, \neg \alpha \vdash \Delta$}\DisplayProof$ \\ 
    \end{tabular}
       
    \item  If  $f = f_{F\neg}$:\\
    
    \begin{tabular}{lll}

       $\AxiomC{$\mathcal{T}( f(F \alpha,L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
       %$=\AxiomC{$\mathcal{T}( (L-F\neg \alpha):F \neg \alpha:T \alpha)$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
       &$=\AxiomC{$\Gamma ,\neg \alpha \vdash \neg \alpha, \Delta$}\doubleLine\UnaryInfC{$\Gamma \vdash , \neg \alpha \Delta$}\DisplayProof$ \\
       &$=\RightLabel{\scriptsize{$\neg$L}}\AxiomC{$\Gamma , \alpha \vdash \neg \alpha, \Delta$}\UnaryInfC{$\Gamma \vdash \neg \alpha , \neg \alpha \Delta$}\UnaryInfC{$\Gamma,  \vdash  \neg \alpha \Delta$}\DisplayProof$ 
    \end{tabular}   

    \item  If  $f = f_{T\land}$:\\
    \begin{tabular}{lll}

       $\AxiomC{$\mathcal{T}( f(T(\alpha \land \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
       %$=\AxiomC{$\mathcal{T}( (L-T(\alpha \land \beta)):\alpha \land \beta:T \alpha:T \beta)$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$
       &$=\AxiomC{$\Gamma ,\alpha, \beta, \alpha \land \beta \vdash \Delta$}\doubleLine\UnaryInfC{$\Gamma, \alpha \land \beta \vdash \Delta$}\DisplayProof$ \\
       &$=\RightLabel{\scriptsize{$\land$L}}\AxiomC{$\Gamma ,\alpha, \beta \vdash \Delta$}\UnaryInfC{$\Gamma, \alpha, \beta, \alpha \land \beta \vdash \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma, \alpha \land \beta \vdash \Delta$}\DisplayProof$
    \end{tabular}  
      
    \item  If  $f = f_{F\land}$:\\
    \begin{tabular}{lll}
       $\AxiomC{$\mathcal{T}( f(F(\alpha \land \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
       %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : F \alpha) $}\AxiomC{$\mathcal{T}( L - \sigma: \sigma : F \beta) $}\doubleLine\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$
       
       
       &$=\AxiomC{$\Gamma ,\alpha, \alpha \land \beta \vdash \Delta$}\AxiomC{$\Gamma , \beta, \alpha \land \beta \vdash \Delta$}\doubleLine\BinaryInfC{$\Gamma,\vdash  \alpha \land \beta  ,\Delta$}\DisplayProof$ \\
       &$=\RightLabel{\scriptsize{$\land$R}}\AxiomC{$\Gamma ,\alpha, \alpha \land \beta \vdash \Delta$}\AxiomC{$\Gamma , \beta, \alpha \land \beta \vdash \Delta$}\BinaryInfC{$\Gamma \vdash  \alpha \land \beta ,\alpha \land \beta, \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma,\vdash  \alpha \land \beta  ,\Delta$}\DisplayProof$
    \end{tabular}  
       
    \item  If  $f = f_{T\lor}$:\\
    \begin{tabular}{lll}
   $\AxiomC{$\mathcal{T}( f(T(\alpha \lor \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : T \alpha)$}\AxiomC{$\mathcal{T}( L - \sigma: \sigma : T \beta)$}\doubleLine\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$
   &$=\AxiomC{$\Gamma ,\alpha , \alpha \lor \beta \vdash \Delta$}\AxiomC{$\Gamma ,\beta, \alpha \lor \beta \vdash \Delta$}\doubleLine\BinaryInfC{$\Gamma, \alpha \lor \beta \vdash \Delta$}\DisplayProof$\\
   &$=\RightLabel{\scriptsize{$\lor$L}} \AxiomC{$\Gamma ,\alpha \vdash  \alpha \lor \beta,\Delta$}\AxiomC{$\Gamma , \beta, \alpha \lor \beta \vdash \Delta$}\BinaryInfC{$\Gamma \vdash  \alpha \lor \beta,\alpha \lor \beta ,\Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma \vdash  \alpha \lor \beta ,\Delta$}\DisplayProof$
    \end{tabular}

    \item  If  $f = f_{F\lor}$:\\
    \begin{tabular}{lll}
    $\AxiomC{$\mathcal{T}( f(F(\alpha \lor \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$ 
    &$=\AxiomC{$\Gamma \vdash \alpha \lor \beta,\alpha,\beta,\Delta$}\doubleLine\UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$\\
    &$=\AxiomC{$\Gamma \vdash \alpha \lor \beta,\alpha,\beta,\Delta$}\RightLabel{\scriptsize{$\lor R_1$}}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta,\alpha \lor \beta,\beta \Delta$}\RightLabel{\scriptsize{$\lor R_2$}}\UnaryInfC{$\Gamma \vdash \alpha \lor \beta,\alpha \lor \beta,\alpha \lor \beta \Delta$} \RightLabel{\scriptsize{contraction}} \UnaryInfC{$\Gamma \vdash \alpha \lor \beta,\alpha \lor \beta , \Delta$}\RightLabel{\scriptsize{contraction}} \UnaryInfC{$\Gamma \vdash \alpha \lor \beta, \Delta$}\DisplayProof$
    \end{tabular}
   
   \item  If  $f = f_{T\rightarrow}$:\\
   \begin{tabular}{lll}
   
   $\AxiomC{$\mathcal{T}( f(T(\alpha \rightarrow \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : F \alpha )$}\AxiomC{$\mathcal{T}( L - \sigma: \sigma : T \beta ) $}\doubleLine\BinaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   &$=\AxiomC{$\Gamma, \alpha, \alpha \rightarrow \beta \vdash \Delta$}\AxiomC{$\Gamma, \alpha \rightarrow \beta \vdash  \beta, \Delta$}\doubleLine\BinaryInfC{$\Gamma, \alpha \rightarrow \beta \vdash \Delta$}\DisplayProof$  \\
   &$=\RightLabel{\scriptsize{$\rightarrow$L}}\AxiomC{$\Gamma, \alpha, \alpha \rightarrow \beta \vdash \Delta$}\AxiomC{$\Gamma, \alpha \rightarrow \beta \vdash  \beta, \Delta$}\BinaryInfC{$\Gamma, \alpha \rightarrow \beta,\alpha \rightarrow \beta  \vdash \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma, \alpha \rightarrow \beta \vdash \Delta$}\DisplayProof$  
   
   \end{tabular}

   \item  If  $f = f_{F\rightarrow}$:\\
   \begin{tabular}{lll}
   $\AxiomC{$\mathcal{T}( f(F(\alpha \rightarrow \beta),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}((L - F(\alpha \rightarrow \beta)) : F(\alpha \rightarrow \beta) : T \alpha : F \beta)$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   
   
   &$=\AxiomC{$\Gamma , \alpha \vdash \beta, \alpha \rightarrow \beta, \Delta$}\doubleLine\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \Delta$}\DisplayProof$\\
   &$=\RightLabel{\scriptsize{$\rightarrow$R}}\AxiomC{$\Gamma , \alpha \vdash \beta, \alpha \rightarrow \beta, \Delta$}\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \alpha \rightarrow \beta, \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma \vdash \alpha \rightarrow \beta, \Delta$}\DisplayProof$
   
   \end{tabular}


   \item  If  $f = f_{T\forall}$:\\
   \begin{tabular}{lll}
   $\AxiomC{$\mathcal{T}( f(T(\forall x \, \phi(x)),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : T \phi(c_i) )$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   
   
   &$=\AxiomC{$\Gamma, \forall x \, \phi(x), \phi(c_i) \vdash \Delta$}\doubleLine\UnaryInfC{$\Gamma, \forall x \, \phi(x) \vdash \Delta$}\DisplayProof$  \\
   &$=\RightLabel{\scriptsize{$\forall$L}}\AxiomC{$\Gamma, \forall x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \forall x \, \phi(x), \forall x \, \phi(x) \vdash \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma, \forall x \, \phi(x) \vdash \Delta$}\DisplayProof$
   
   \end{tabular}

   


   \item  If  $f = f_{F\forall}$:\\
   \begin{tabular}{lll}
   $\AxiomC{$\mathcal{T}( f(F(\forall x \, \phi(x)),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : F \phi(c_i) )$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   
   
   &$=\AxiomC{$\Gamma \vdash \phi(c_i), \forall x \, \phi(x), \Delta$}\doubleLine\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \Delta$}\DisplayProof$  \\
   &$=\RightLabel{\scriptsize{$\forall$R}}\AxiomC{$\Gamma \vdash \phi(c_i), \forall x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \forall x \, \phi(x), \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma \vdash \forall x \, \phi(x), \Delta$}\DisplayProof$
   
   $c_i$ not in $\Gamma$ or $\Delta$, as it is not in $L-\sigma$, fresh


   \end{tabular}


   
   \item  If  $f = f_{T\exists}$:\\
   \begin{tabular}{lll}
   $\AxiomC{$\mathcal{T}( f(T(\exists x \, \phi(x)),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : T \phi(c_i) )$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   
   
   &$=\AxiomC{$\Gamma, \exists x \, \phi(x), \phi(c_i) \vdash \Delta$}\doubleLine\UnaryInfC{$\Gamma, \exists x \, \phi(x) \vdash \Delta$}\DisplayProof$  \\
   &$=\RightLabel{\scriptsize{$\exists$L}}\AxiomC{$\Gamma, \exists x \, \phi(x), \phi(c_i) \vdash \Delta$}\UnaryInfC{$\Gamma, \exists x \, \phi(x), \exists x \, \phi(x) \vdash \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma, \exists x \, \phi(x) \vdash \Delta$}\DisplayProof$
   

   \end{tabular}
   
   $c_i$ not in $\Gamma$ or $\Delta$, as it is not in $L-\sigma$, fresh

   
   \item  If  $f = f_{F\exists}$:\\
   \begin{tabular}{lll}

   $\AxiomC{$\mathcal{T}( f(F(\exists x \, \phi(x)),L))$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   %$=\AxiomC{$\mathcal{T}( L - \sigma: \sigma : F \phi(c_i) )$}\doubleLine\UnaryInfC{$\mathcal{T}(L)$}\DisplayProof$  
   
   
   &$=\AxiomC{$\Gamma \vdash \phi(c_i), \exists x \, \phi(x), \Delta$}\doubleLine\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \Delta$}\DisplayProof$  \\
   &$=\RightLabel{\scriptsize{$\exists$R}}\AxiomC{$\Gamma \vdash \phi(c_i), \exists x \, \phi(x), \Delta$}\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \exists x \, \phi(x), \Delta$}\RightLabel{\scriptsize{contraction}}\UnaryInfC{$\Gamma \vdash \exists x \, \phi(x), \Delta$}\DisplayProof$
   \end{tabular}
   \end  {itemize}
   }
       
   
   \end{proof}
}

\def\TranslationClassical{
\begin{definition} \textbf{Tree Translating Function}
    Given a tableaux proof-tree development $\tau$ and its root r , we define $\mathcal{T}_p(\tau)$:
    \begin{itemize}
        \item If $\tau$ = r and there are $T \sigma $ and $F \sigma $ on r:
        
        $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Ax $\sigma$}}\AxiomC{}\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$
        \item If $\tau$ = r and there is no $\sigma$ such that $T \sigma $ and $F \sigma $ are on r: 
        
        $\mathcal{T}_p(\tau) = \mathcal{T}(\tau) $

        \item If $r$ has a single child $r_0$ with a corresponding subtree $\tau_0$: \\by definition, it exists a sentence $\sigma$ such that  
        $f(\sigma,r)=f_{Rule}(\sigma,r)=r_0$ , and $r_0$ is the root of $\mathcal{T}_0$,  so 
        
        
        $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on  $\sigma$}}\AxiomC{$\mathcal{T}_p(\tau_0)$}\doubleLine\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$. 
        \item If $r$ has two children $r_1$ and $r_2$ with corresponding subtrees $\tau_1$ and $\tau_2$:\\ by definition there exists a sentence $\sigma$  such that
            $f(\sigma, r) = f_{Rule}(\sigma, r) = \{r_1, r_2\}$, and so:


            $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on $\sigma$}}\AxiomC{$\mathcal{T}_p(\tau_1)$}\AxiomC{$\mathcal{T}_p(\tau_2)$}\doubleLine\BinaryInfC{$\mathcal{T}(r)$}\DisplayProof$ 
    \end{itemize}
\end{definition}
}

\def\TranslationClassicalProof{
    \begin{theorem}
        Given a classical tableaux development $\tau$, $\mathcal{T}_p(\tau)$ is a valid sequent proof-tree development. 
    \end{theorem}
    \begin{proof}
        Here r is the root of $\tau$. The proof goes by induction on the size of $\tau$:
        \begin{itemize}
            \item if $\tau$ = r and there are    $T \sigma $ and $F \sigma $ on r, $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Ax $\sigma$}}\AxiomC{}\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$ is a valid sequent proof.
            \item if $\tau$ = r and there are no $T \sigma $ and $F \sigma $ on r, $\mathcal{T}_p(\tau) = \AxiomC{$\mathcal{T}(r)$}\DisplayProof$ is a valid sequent proof.
            \item if $r$ has a single child $r_0$ with a corresponding subtree $\tau_0$: 
             $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on  $\sigma$}}\doubleLine\AxiomC{$\mathcal{T}_p(\tau_0)$}\UnaryInfC{$\mathcal{T}(r)$}\DisplayProof$
              is a valid sequent proof since $\mathcal{T}_p(\tau_0)$ is valid by induction hypothesis and the rule is admissible by the Theroem 4.
            \item if $r$ has two children $r_1$ and $r_2$ with corresponding subtrees $\tau_1$ and $\tau_2$:\\ 
                $\mathcal{T}_p(\tau) = \RightLabel{\scriptsize{Rule on $\sigma$}}\doubleLine\AxiomC{$\mathcal{T}_p(\tau_1)$}\AxiomC{$\mathcal{T}_p(\tau_2)$}\BinaryInfC{$\mathcal{T}(r)$}\DisplayProof$ 
                is a valid sequent proof since $\mathcal{T}_p(\tau_1)$ and $\mathcal{T}_p(\tau_2)$ are valid by induction hypothesis and the rule is admissible by the Theroem 4.
\hfill $\Box$
        \end{itemize}
    
    \end{proof}
}


\def\ThinningFunctionDefinition{
\begin{definition} \textbf{Tree Thinning Function}
    Given an intuitionistic tableaux proof-tree development and its root r , we define $\mathcal{F}(\tau)$ ($\mathcal{F}: tree \rightarrow tree $):
    \begin{itemize}
        \item If $\tau$ = r then there are $T_f \sigma $ and $F_f \sigma $ on r:
        
        $\mathcal{F}(\tau) = [T_f \sigma   , F_f \sigma ]$
 

        \item If $r$ has a single child $f(\sigma,r)$ 
        
        with a corresponding sub-tree $\tau_0$ and  $r'_0$ is the root of $\mathcal{F}(\tau_0)$:


         $(f(\sigma,r) - r)$  are the elements generated by the inference f and 


         $r'_0 $ are the elements necessary on the thinned proof $\mathcal{F}(\tau_0)$.


          In this case:
         \begin{itemize}
        \item
         If $(f(\sigma,r) - r) \cap r'_0 \neq \emptyset $
         
         $\mathcal{F}(\tau) $ = a tree with root $(r'_0 - f(\sigma,[\sigma])):\sigma$ connected to the child $r'_0 :(f(\sigma,[\sigma])-\sigma)$,  that has as a child the sub-tree $\mathcal{F}(\tau_0)$
         \item
         If $(f(\sigma,r) - r) \cap r'_0 = \emptyset $

         
         $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_0)$
         \end{itemize}


         \item If $r$ has the children $f(\sigma,r)[1]$ and $f(\sigma,r)[2]$ 
         
         with the corresponding sub-trees $\tau_1$ and $\tau_2$,  $r'_1$ is the root of $\mathcal{F}(\tau_1)$ and $r'_2$ is the root of $\mathcal{F}(\tau_2)$, 
         then $((f(\sigma,r)[1] - r)\cap r'_1)  \cup ((f(\sigma,r)[2] - r)\cap r'_2)$ also defines if f was "useful":


         
         \begin{itemize}
            \item
            % If $((f(\sigma,r)[1] - r)\cap r'_1)  \cup ((f(\sigma,r)[2] - r)\cap r'_2) \neq \emptyset $:

             If $((f(\sigma,r)[1] - r)\cap r'_1)  = \emptyset $:
             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_1) $
             \item 
             If $((f(\sigma,r)[2] - r)\cap r'_2)  = \emptyset $:
             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_2) $
             \item Otherwise:  
             $\mathcal{F}(\tau) $ = a tree with root $(r'_1 - f(\sigma,[\sigma])[1]) : (r'_2 - f(\sigma,[\sigma])[2]):\sigma$  connected to the children $r'_1 :(f(\sigma,[\sigma])[1]-\sigma)$  and $r'_2 :(f(\sigma,[\sigma])[2]-\sigma)$, each having 
             $\mathcal{F}(\tau_1)$ and $\mathcal{F}(\tau_2)$, respectively, below them. 
        \end{itemize}
    

    \end{itemize}
\end{definition}
}




\def\thinnedInvalidityproof{
    \begin{theorem}
        Given a tableaux proof $\tau$, the root $r'$ of $\mathcal{F}(\tau)$ is intuitionistically invalid 
    \end{theorem}
    \begin{proof}

        The proof goes by induction on the size of $\tau$:
        \begin{itemize}
            \item If $\tau$ = r, $\mathcal{F}(\tau) = [T_f \sigma   , F_f \sigma ]$.  The theorem holds
     
    
            \item If $r$ has a single child $f(\sigma,r)$ 
            
            with a corresponding sub-tree $\tau_0$ and  $r'_0$ is the root of $\mathcal{F}(\tau_0)$:
    
    
            \begin{itemize}
            \item
             If $(f(\sigma,r) - r) \cap r'_0 \neq \emptyset $:
             $\mathcal{F}(\tau) $  has the root $(r'_0 - f(\sigma,[\sigma])):\sigma$    


             
             By induction hypothesis, we know $r'_0$ to be intuitionistically invalid. We also know that the intuitionistic validity of $\sigma$ 
             implies the intuitionistic validity of  $f(\sigma,[\sigma])$:


             
             Assume $r'$ to be valid, then $f(\sigma,r')$  should be valid then $r'_0$ should be also valid, (as $r'_0 \supseteq  f(\sigma,r')$).This contradicts the induction hypothesis. 
             

             \item
             If $(f(\sigma,r) - r) \cap r'_0 = \emptyset $ 

             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_0)$

             And, by induction hypothesis, we know $r'_0$ to be intuitionistically invalid
             \end{itemize}
         \item if $r$ has the children $f(\sigma,r)[1]$ and $f(\sigma,r)[2]$ :
         
         \begin{itemize}
            \item
             If $(f(\sigma,r) - r) \cap (r'_1 \cup r'_2 ) \neq \emptyset $:
             
             $\mathcal{F}(\tau) $ has the root $(r'_0 - f(\sigma,[\sigma])):\sigma$ , Assume $r'$ to be valid, 
             then either $f(\sigma,r')$[1] or $f(\sigma,r')$[2]  should be intuitionistically valid then either $r'_1 \supseteq  f(\sigma,r')[2]$ or $r'_1 \supseteq  f(\sigma,r')[2]$ should be intuitionistically valid. 
             We know, by induction hypothesis, that both are intuitionistically invalid, which yields a contradiction.

             \item
             If $(f(\sigma,r) - r) \cap (\mathcal{F}(r'_1) \cup \mathcal{F}(r'_2) ) = \emptyset $: 
             
             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_1) $ is valid by induction hypothesis.  \hfill $\Box$
        \end{itemize}
    
        \end{itemize}
    
    \end{proof}
}



\def\thinnedsizeproof{
    \begin{theorem}
       If a tableaux proof-tree $\tau$ does not branch, the root $r'$ of $\mathcal{F}(\tau)$  has not more than 2 signed sentences  
    \end{theorem}
    \begin{proof}
      
        
        The proof goes by induction on the size of $\tau$:
        \begin{itemize}
            \item If $\tau$ = r, $\mathcal{F}(\tau) = [T_f \sigma   , F_f \sigma ]$.  The theorem holds
     
    
            \item If $r$ has a single child $f(\sigma,r)$ :
            
            with a corresponding sub-tree $\tau_0$ and  $r'_0$ is the root of $\mathcal{F}(\tau_0)$:
    
    
            \begin{itemize}
            \item
             If $(f(\sigma,r) - r) \cap r'_0 \neq \emptyset $:
             
             the root $r'$ of $\mathcal{F}(\tau) $ is $(r'_0 - f(\sigma,[\sigma])):\sigma$ 
             
            
             by induction hypothesis $\#(r'_0) \leq 2$ and so $\#[ (r'_0 - f(\sigma,[\sigma])):\sigma ] \leq 2$ 
            
             \item
             If $(f(\sigma,r) - r) \cap r'_0 = \emptyset $
             
             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_0)$


              and so $\#(r') = \#(r'_0) \leq 2$ \hfill $\Box$
    
             \end{itemize}    
        \end{itemize}
    \end{proof}
}




\def\nnnFProof{
    \begin{theorem}
       (proof/search for a counter ex) If a tableaux proof $\tau$ does not branch, the root $r'$ of $\mathcal{F}(\tau)$  has not more than 1 signed sentences $F$  
    \end{theorem}

    Assume that $r'$ has more than 1 signed sentences of type $F$, 
    by the previous theorems, $r' = [F_p A , F_q B]$ and is intuitionistically invalid. 
    
    By theorem [], $\mathcal{T}(min(p,q),[F_p A , F_q B]) = \vdash A,B$ is valid . Thus, either $\vdash B$ or
    $\vdash A$ is valid. That leads to a contradiction, as if $r'=[F_p A]$ is invalid then the "useless"  $F_q B$ should not be in r'.
}


\def\nnnnFProof{
    \begin{theorem}
        Given a tableaux proof $\tau$, the root $r'$ of $\mathcal{F}(\tau)$ is intuitionistically invalid 
    \end{theorem}
    \begin{proof}

        The proof goes by induction on the size of $\tau$:
        \begin{itemize}
            \item If $\tau$ = r, $\mathcal{F}(\tau) = [T_f \sigma   , F_f \sigma ]$.  The theorem holds
     
    
            \item If $r$ has a single child $f(\sigma,r)$ :
            
            with a corresponding sub-tree $\tau_0$ and  $r'_0$ is the root of $\mathcal{F}(\tau_0)$:
    
    
            \begin{itemize}
            \item
             If $(f(\sigma,r) - r) \cap r'_0 \neq \emptyset $:
             $\mathcal{F}(\tau) $ = a tree with root $(r'_0 - f(\sigma,[\sigma])):\sigma$ connected to the child $r'_0 :(f(\sigma,[\sigma])-\sigma)$,  that has as a child the sub-tree $\mathcal{F}(\tau_0)$
   
             
             By induction hypothesis, we know $r'_0$ to . We also know that the intuitionistic validity of $\sigma$ 
             implies the intuitionistic validity of  $f(\sigma,[\sigma])$:


             
             Assume $r'$ to be valid, then $f(\sigma,r')$  should be valid then $r'_0 \supseteq  f(\sigma,r')$ should be also valid 
             

             \item
             If $(f(\sigma,r) - r) \cap r'_0 = \emptyset $ 

             $\mathcal{F}(\tau) $ = $\mathcal{F}(\tau_0)$

             And, by induction hypothesis, we know $r'_0$ to be intuitionistically invalid
             \end{itemize}
         \item if $r$ has the children $f(\sigma,r)[1]$ and $f(\sigma,r)[2]$ :
         
        
    
        \end{itemize}
    
    \end{proof}
}






